### 2024-12-03 other/datasheet/datasheet_template.qmd
commit

---
title: "Datasheet for 'Canadian Grocery Price Data'"
author: 
  - Bo Tang
thanks: "Code and data are available at: https://github.com/Botangeric/Beef-Pricing-Dynamics-in-Canadian-Supermarkets/upload/main."
date: "02 December 2024"
format: pdf
number-sections: true
bibliography: references.bib
---

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - This dataset was created to observe price changes in products across eight major supermarkets in Canada, helping people better understand the market.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - Jacob Filipp
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - TBD
4. *Any other comments?*
    - TBD

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- TBD
2. *How many instances are there in total (of each type, if appropriate)?*
	- TBD
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- TBD
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- TBD
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- TBD
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- TBD
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- TBD
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- TBD
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- TBD
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- TBD
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- TBD
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- TBD
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- TBD
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- TBD
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- TBD
16. *Any other comments?*
	- TBD

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- TBD
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- TBD
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- TBD
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- TBD
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- TBD
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- TBD
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- TBD
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- TBD
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- TBD
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- TBD
12. *Any other comments?*
	- TBD

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- TBD
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- TBD
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- TBD
4. *Any other comments?*
	- TBD

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- TBD
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- TBD
3. *What (other) tasks could the dataset be used for?*
	- TBD
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- TBD
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- TBD
6. *Any other comments?*
	- TBD

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- TBD
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- TBD
3. *When will the dataset be distributed?*
	- TBD
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- TBD
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- TBD
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- TBD
7. *Any other comments?*
	- TBD

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- TBD
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- TBD
3. *Is there an erratum? If so, please provide a link or other access point.*
	- TBD
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- TBD
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- TBD
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- TBD
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- TBD
8. *Any other comments?*
	- TBD

\newpage

# References

### 2024-12-03 paper/paper.qmd
commit

---
title: "Beef Pricing Dynamics in Canadian Supermarkets"
author: 
  - Bo Tang
thanks: "Code and data are available at: [https://github.com/Botangeric/Beef-Pricing-Dynamics-in-Canadian-Supermarkets)."
date: today
date-format: long
abstract: "This study examines beef pricing trends in two Canadian supermarkets, T&T and Loblaws, using data from June to November 2024. We found that prices were stable overall, with seasonal increases in winter and significant differences between the supermarkets' pricing strategies. These findings reveal how cultural and operational factors, alongside seasonality, influence consumer pricing. This contributes to a better understanding of market dynamics and economic behavior in Canada."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(broom.mixed)
library(tidyverse)
library(dplyr)
library(knitr)
library(ggplot2)
library(here)
library(kableExtra)
library(arrow)
library(rstanarm)
model <- readRDS("../models/beef_product_model.rds")
cleaned_data <- read_parquet("../data/02-analysis_data/cleaned_data.parquet")
```

# Introduction

Beef is one of the most widely consumed staples in Canada, making it a critical product for understanding consumer behavior, market dynamics, and economic trends. Pricing trends in beef products provide insights into broader economic forces, including the effects of supply chains, consumer preferences, and seasonal variations. Despite its significance, a detailed analysis of beef pricing strategies in major Canadian supermarkets is limited, particularly when considering cultural differences and post-pandemic economic recovery.

This paper focuses on analyzing beef pricing trends in two leading Canadian supermarkets, T&T and Loblaws. These supermarkets cater to distinct consumer groups, with T&T focusing on Asian demographics and Loblaws serving a broader North American audience. By comparing these two supermarkets, we aim to uncover patterns in pricing strategies, seasonal variations, and factors influencing beef prices. The study utilizes a dataset spanning June to November 2024, capturing detailed pricing information across multiple products and months.

A key gap addressed in this paper is the limited understanding of how supermarket-specific strategies and broader economic factors interplay in shaping beef prices. While previous studies have focused on aggregate market trends, few have explored the cultural and operational distinctions between retailers and their implications for pricing. Our analysis fills this gap by incorporating a Bayesian linear regression model to evaluate the impact of vendor type, seasonal trends, and historical pricing on current beef prices.

The results of this study reveal that beef prices were relatively stable during the study period, with limited fluctuations and even discounted prices in some cases. However, significant differences in pricing strategies between T&T and Loblaws reflect cultural and operational distinctions. Furthermore, seasonal variations indicate that winter prices tend to be higher than summer prices, driven by increased demand during holidays and colder weather. These findings underscore the importance of considering both macroeconomic trends and retailer-specific strategies when analyzing pricing dynamics.

The remainder of this paper is structured as follows: [@sec-data] details the dataset and methodology used in this analysis. [@sec-model] describes the Bayesian linear regression model and its setup. [@sec-result] presents the results, highlighting key trends and insights. Finally, [@sec-discussion] discusses the implications of these findings, the limitations of the study, and potential directions for future research.

# Data {#sec-data}

## Overview
The data for this study came from Project Hammer[@PG].The datasets were cleaned and analysed using the statistical programming software `R` [@citeR] along with the help of `tidyverse` [@citeTidyverse], `knitr` [@citeKnitr], `ggplot2` [@citeGgplot], `here` [@citeHere], `dplyr` [@citeDplyr], `rstanarm` [@citeRstanarm], `arrow` [@citeArrow], `broom.mixed` [@citeBroomMixed] and `kableExtra` [@citeKableExtra].The raw data covers eight major large supermarkets in Canada and the changes in their products between February 28, 2024, and November 26, 2024.

## Measurement

The data was collected by Jacob from the product prices on each supermarket's website, and these prices are all for "in-store pickup".The data we obtained is all based on the prices of products visible to consumers, and we cannot observe the prices at which retailers acquire the goods.

## Outcome variables

The outcome variable, current price, represents the most recent market price of products in the dataset. It serves as a critical metric for understanding pricing strategies, consumer behavior, and market trends. By analyzing current_price, we can evaluate the impact of factors such as discounts (old price), vendor differences, and temporal trends (e.g., month) on product pricing.The line graph [@fig-current] illustrates the average monthly current_price trend across the dataset. The most notable pattern is the significant drop in prices between months 6 and 8, reaching the lowest average in month 8. This is followed by a steady upward trend, with prices gradually increasing and peaking in month 11.

This trend likely reflects seasonal or market dynamics that influence product pricing. The decline in prices during the mid-year months could indicate promotional events, seasonal sales, or a decrease in consumer demand during that period. Conversely, the rise in prices from months 9 to 11 may correspond to increased demand, possibly due to holiday preparations or end-of-year market adjustments.

```{r}
#| label: fig-current
#| fig-cap: Current Price Distribution Across Months
#| echo: false

# Group by month and calculate the overall average price
monthly_price_trend <- cleaned_data %>%
  group_by(month) %>%
  summarize(average_price = mean(current_price, na.rm = TRUE), .groups = "drop")

# Plot the overall price trend
ggplot(monthly_price_trend, aes(x = month, y = average_price)) +
  geom_line(color = "blue") +
  geom_point(color = "blue") +
  labs(
    x = "Month",
    y = "Average Current Price"
  ) +
  theme_minimal()
```

## Predictor variables

Our main predictor variables are vendor, month, and old price.

**Vendor**:This variable represents the seller or distributor of the product.

**Month**:This variable reflects the time of year (e.g., seasonality) and allows us to analyze temporal trends in pricing. It can help identify seasonal effects or promotional periods that impact product prices.

**Old price**:This variable represents the product's previous price. It serves as an indicator of discounts or price changes, which are key factors in determining the current_price. It provides a direct measure of pricing adjustments over time.

### Vendor
The boxplot [@fig-vendor] illustrates the price distribution of beef products by vendor. Loblaws shows a wider range of prices, with several outliers exceeding $100, indicating higher variability in pricing. The median price for Loblaws is lower, with the interquartile range suggesting a focus on moderately priced products, but the presence of outliers points to occasional high-priced items. In contrast, T&T exhibits a more concentrated price distribution, with fewer outliers and a higher median price. The interquartile range for T&T is narrower, indicating a more consistent pricing approach with fewer extreme values. These patterns highlight the differences in the spread and central tendency of prices between the two vendors.

```{r}
#| label: fig-vendor
#| fig-cap: Price Distribution of Beef Products by Vendor
#| echo: false
#| warning: false
#| message: false

# Plot the box plot for price comparison between vendors
ggplot(cleaned_data, aes(x = vendor, y = current_price, fill = vendor)) +
  geom_boxplot(outlier.colour = "red", outlier.size = 2) +
  labs(
    x = "Vendor",
    y = "Current Price"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12),
    legend.position = "none"
  ) +
  scale_fill_manual(values = c("Loblaws" = "blue", "TandT" = "green"))  # Customize colors

```
### Month
@fig-month illustrates the distribution of current prices across months, showing variations in the median price, interquartile range, and outliers for each month. The median price remains relatively consistent throughout the months, with slight increases observed in later months (e.g., 10 and 11). The interquartile range is narrow across all months, indicating that most prices are clustered within a specific range. However, outliers are present in every month, with several extreme values exceeding 50 and even 100 in some cases, particularly in months 7 and 10. This suggests that while the majority of prices are stable, there are occasional high-priced products influencing the distribution. The overall pattern suggests minor fluctuations in price distribution across the observed months.

```{r}
#| label: fig-month
#| fig-cap: Current Price Distribution Across Months
#| echo: false
#| warning: false
#| message: false
# Create the box plot
ggplot(cleaned_data, aes(x = factor(month), y = current_price, fill = factor(month))) +
  geom_boxplot(outlier.colour = "red", outlier.size = 2) +
  labs(
    x = "Month",
    y = "Current Price",
    fill = "Month"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12)
  ) +
  scale_fill_brewer(palette = "Set3")  # Use a predefined color palette
```
### old price
The scatterplot compares current prices against old prices for products, showing a strong positive relationship between the two variables. Most points cluster near the red dashed line (representing equality between current and old prices), indicating that current prices often closely follow old prices. However, there are noticeable deviations where current prices are lower than old prices, which suggests discounts or price reductions. A few outliers, particularly for old prices exceeding 100, show significant variance, with current prices remaining below the old prices. This pattern highlights that while prices generally follow historical trends, discounts and occasional large price differences exist.

```{r}
#| label: fig-old
#| fig-cap: Comparison of Current Price vs Old Price
#| echo: false
#| warning: false
#| message: false
# Create the scatter plot
ggplot(cleaned_data, aes(x = old_price, y = current_price)) +
  geom_point(alpha = 0.6, color = "blue", size = 2) +
  labs(
    x = "Old Price",
    y = "Current Price"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 12)
  ) +
  geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") # Add a reference line

```

# Model {#sec-model}

## Model overveiw

The model is a Bayesian linear regression that predicts the current price of beef products. It uses the scaled old price old price as a numerical variable and includes vendor and month as categorical variables. This setup allows the model to account for the effects of historical prices, differences between supermarkets, and seasonal variations.

## Model set-up
We set current price to be Y,Old price to be X,Vendor to be Z,month to be H,The linear regression model I will be using is:
$$
\begin{aligned}
Y = \beta_0 + \beta_1 \cdot X + \beta_2 \cdot Z + \beta_3 \cdot H
\end{aligned}
$$
$$
\begin{aligned}
\beta_0 & \sim \mbox{Normal}(0, 2.5)\\
\beta_1 & \sim \mbox{Normal}(0, 2.5)\\
\beta_2 & \sim \mbox{Normal}(0, 2.5)\\
\beta_3 & \sim \mbox{Normal}(0, 2.5)\\
\end{aligned}
$$
Where,

- $\beta_0$ The intercept term, indicating the baseline price when all predictors are at their reference levels.
- $\beta_1$ The coefficient for old_price, representing the linear effect of the old price on the current price.
- $\beta_2$ The coefficient for vendor, representing the effect of different vendors on the current price (a categorical variable encoded as dummy variables).
- $\beta_3$ The coefficient for month, representing the effect of different months on the current price (a categorical variable encoded as dummy variables).

In my model, normal priors with a mean of 0 and a standard deviation of 2.5 are used for the coefficients. This choice implies no specific expectation regarding the direction or magnitude of the relationships between the predictors and the dependent variable. I selected these priors because I do not have strong prior knowledge about the likely effect sizes in this context.

The standard deviation of 2.5 represents a moderately wide prior, reflecting uncertainty in the prior beliefs. This ensures that the priors are weakly informative, allowing the data to play the dominant role in determining the posterior distributions.

The chosen priors also serve to regularize the model by limiting the potential for extreme coefficient estimates, which can arise due to noise or limited sample sizes. This regularization helps stabilize the model and improves its ability to generalize to new data, particularly when there are potential multicollinearity issues or when the dataset is small.

## Model Limitatioin

A limitation of the model is that it is entirely trained on a single dataset without splitting it into training and testing subsets. While this approach ensures all data contributes to parameter estimation, it limits the ability to validate predictions on unseen data, potentially impacting generalizability. Additionally, the model only considers three predictors—old price, vendor, and month—while other factors, such as production costs, supply chain disruptions, or regional economic conditions, may also influence beef prices but are not included. Furthermore, the dataset covers only a six-month period in 2024, restricting the model's applicability to other timeframes or broader market contexts.

## Model justification

The Bayesian linear regression model was selected for this analysis due to its flexibility and ability to incorporate prior knowledge. This model allows us to estimate the effect of historical prices, vendor strategies, and seasonal trends on beef pricing while accounting for uncertainty in the estimates. The choice of predictors, including scaled old prices, vendor, and month, aligns with established theories in market dynamics and consumer behavior, ensuring the model is grounded in sound reasoning.

A Bayesian approach was particularly suitable for this dataset, as it balances interpretability with predictive accuracy. By using priors, the model prevents overfitting and provides robust estimates even with limited data. This framework also enables us to quantify uncertainty in the predictions through posterior distributions, offering richer insights compared to traditional regression methods. Additionally, the inclusion of categorical variables (vendor and month) and a continuous predictor (scaled old prices) makes the model versatile for capturing both fixed and dynamic aspects of pricing. These attributes make Bayesian linear regression the optimal choice for this analysis.

# Results {#sec-result}

@fig-model-coefficients illustrates the coefficients and their corresponding 95% credible intervals for the predictor variables in the Bayesian model. A 95% credible interval means that there is a 95% probability that the true parameter lies within the interval, given the observed data and the model assumptions.

Each point represents the estimated coefficient for a predictor variable, with the horizontal lines indicating the credible interval around the estimate. Variables with coefficients to the right of zero indicate a positive association with the outcome variable, suggesting that an increase in the predictor variable corresponds to an increase in the outcome variable. Conversely, coefficients to the left of zero indicate a negative association, implying that an increase in the predictor variable is associated with a decrease in the outcome variable. Variables whose credible intervals include zero indicate that their effect on the outcome is uncertain or not statistically significant.

The results show that old price scaled is a significant positive factor influencing the current price, with its credible interval entirely to the right of zero, indicating that higher old prices are associated with higher current prices. In contrast, the coefficients for vendor "TandT" and most month variables have credible intervals that include zero, suggesting their effects on current price are weak or uncertain. Additionally, the intercept has a high estimate with a credible interval far from zero, highlighting the significant role of the baseline price in the model.

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-model-coefficients
#| fig-cap: Model Coefficients with 95% Credible Intervals

# Extract coefficients and credible intervals
coefficients <- broom::tidy(model, conf.int = TRUE)

# Plot coefficients
ggplot(coefficients, aes(x = estimate, y = term)) +
  geom_point() + # Coefficient points
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high)) + # Credible intervals
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") + # Zero line
  labs(
    x = "Coefficient Estimate",
    y = "Predictor"
  ) +
  theme_minimal()
``` 
@fig-current In the data section, we can observe that beef products exhibit clear seasonal price patterns. During summer, the prices of beef products are significantly lower compared to winter, which may be due to seasonal demand changes and the impact of holidays. For example, in winter, the demand for beef products is typically higher, possibly driven by a preference for high-calorie foods during colder weather. Additionally, most major holidays, such as Christmas and Thanksgiving, occur in winter, further boosting the demand for beef products and leading to price increases.

@fig-vendor illustrates the price distribution of beef products by vendor using boxplots for Loblaws and TandT. The y-axis represents the current price, while the x-axis groups prices by vendor. Loblaws exhibits a much wider price range, with numerous outliers far beyond the interquartile range (IQR), and some prices exceeding 100 units. In contrast, TandT has a narrower distribution, with most prices concentrated within a smaller range and fewer extreme outliers.

As a local supermarket, Loblaws offers a diverse selection of beef products with significant price variation, catering to a broad spectrum of consumers, from those seeking affordable options to those purchasing high-end products. This results in a broader price distribution and a greater number of high-price outliers. TandT, an Asian supermarket, focuses on a more specific product line tailored to the preferences of Asian consumers, leading to a more consistent and concentrated price range with fewer outliers.

@fig-old compares the current prices of products to their old prices. Most points are concentrated near the 1:1 red dashed line, indicating that current prices are generally close to old prices. However, there is a noticeable trend where current prices tend to be slightly lower, suggesting a general price reduction across products. A few outliers show significant deviations, where some products experienced substantial price cuts or increases. This indicates a mix of market factors, such as promotions or pricing adjustments. Overall, the data reflects a slight downward shift in prices, with a few exceptions warranting further investigation.

# Discussion {#sec-discussion}

## The pricing situation of beef products

In this article, I aim to analyze the pricing of beef products in two major supermarkets, T&T and Loblaws. I chose beef products because they are one of the main staples consumed by people living in Canada. Changes in their prices can reflect not only market conditions but also broader economic trends.

After studying and analyzing the data, I found that during the time frame provided by the raw data (June to November 2024), the prices of beef products were relatively stable. Price fluctuations were minimal, and there was no significant increase. In fact, some products were sold at discounted prices, which were significantly lower than their original prices. Additionally, my research revealed substantial differences in pricing strategies between the two supermarkets. These differences can be attributed to the fact that the two supermarkets target distinct consumer groups—Loblaws caters primarily to a North American audience, while T&T serves an Asian demographic. These differences in cultural preferences and business strategies result in variations in the pricing of beef products between the two supermarkets.Moreover, beef is a highly seasonal product. As observed in the analysis above, the price of beef in winter is approximately $1 higher than in summer, and as temperatures warm up, the prices decrease again.

## Post-Pandemic Economic Recovery and Rising Beef Prices

When I further researched online, I found that even in 2024, a year when beef prices remained relatively stable, they were still higher compared to previous years. Why does this happen? I believe it is because, after the pandemic, the global economy has been undergoing a recovery period, and the impacts of COVID-19 have not completely disappeared even today. Under such circumstances, factors such as labor costs, feed costs, and transportation costs—which all contribute to the price consumers pay for beef products—have increased. This, in turn, has indirectly forced consumers to spend more to purchase the same beef products.

## Weaknesses and Limitations

In this study, we chose to focus on only two supermarkets, T&T and Loblaws, to control the sample size. While this approach helps streamline our analysis, it also limits the generalizability of our findings, as the data may not represent the broader Canadian beef market. Additionally, in handling missing values, we opted for direct removal, which, while simplifying the data processing, might have introduced bias and reduced the robustness of the dataset.

Our analysis of factors influencing beef prices focused on three variables: month, vendors, and old price. However, beef prices are shaped by a wide array of factors beyond these three. For instance, the costs associated with bringing beef products to market—such as labor, transportation, and feeding costs—as well as external influences like government market policies and supermarket business strategies, all play a role. By simplifying the analysis to these three variables, our study may lack the depth required to produce authoritative predictions about beef pricing.

Furthermore, our dataset is restricted to the year 2024, which limits the applicability of the model to other years. Beef prices vary significantly from year to year due to both predictable factors (such as seasonal trends) and unforeseen circumstances (such as economic disruptions or policy changes). Consequently, our model is best suited for predicting beef prices in 2024 within regions of Canada where T&T and Loblaws operate. Extrapolation to other years or locations should be approached with caution.

## Future Directions
Future research could expand the scope to include more vendors, product categories, and regional variations to provide a broader understanding of market dynamics. Incorporating external factors, such as economic conditions, consumer spending habits, and supply chain disruptions, could enhance the model's explanatory power. Moreover, applying more granular time-series analysis or hierarchical modeling approaches could uncover detailed temporal patterns and interactions between predictors.
Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

## Analysis dataset
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-survey
#| tbl-cap: Analysis dataset

# Glimpse of the anaysis dataset
head(cleaned_data) %>%
  kable(digits = 2)
```
@tbl-survey provides a glimpse of the dataset used for analysis.

## Data cleaning

After obtaining the raw data, I realized that the sample size was too large, with over 10 million rows. Therefore, I decided to focus primarily on the beef product prices of the two supermarkets, "T&T" and "Loblaws". These two supermarkets are more popular and offer a relatively rich variety of beef products. I chose beef products because, in daily life, beef is one of the main foods consumed by people, and changes in its price can reflect certain social conditions.

I also processed the dates, focusing primarily on monthly changes. I simplified the nowtime variable to retain only the month. Additionally, some data in the dataset contained missing values. However, when reviewing the raw data, I observed that for the same product within the same month, the current_price and old_price were relatively consistent. For example, if there was complete data on the 1st of the month, missing data on the 4th, and complete data again on the 10th, the values on the 1st and the 10th were identical. Therefore, to control the sample size, I chose to directly remove entries with missing values.After handling this, it will not have a significant impact on my monthly figures.

# Model details {#sec-model-details}

## Model summary
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-model-coefficients
#| tbl-cap: Summary of the model

# Extract coefficients
library(broom)  # For tidy summary
library(kableExtra)  # For formatted table

# Extract model coefficients with credible intervals
coefficients <- broom::tidy(model, conf.int = TRUE)

# Display coefficients in a neat table with 2 decimal places
coefficients |>
  kable(digits = 2)
```

@tbl-model-coefficients summarizes the results of the Bayesian model, providing key insights into the model's parameters. The Estimate column represents the posterior mean of each parameter, indicating its effect size on the outcome variable. The Standard Error (SE) measures the precision of these estimates, reflecting the variability of the sample statistics. The 95% Credible Interval (CI) shows the range within which the parameter lies with 95% probability, given the observed data and prior distributions. Additionally, diagnostic metrics like Rhat assess the convergence of the model, while Effective Sample Size (ESS) ensures the reliability of the posterior samples. This table offers a comprehensive view of the model's performance and parameter estimates.

## Posterior predictive check
```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-post
#| fig-cap: Posterior distribution for regression model

# Posterior check
pp_check(model)+theme_classic()+theme(legend.position = "bottom")

``` 
@fig-post The observed data (dark curve) and the predictive data (light curve) are largely aligned, suggesting that the model captures the central features of the data reasonably well.
Deviations between the two curves may indicate areas where the model struggles to replicate certain patterns in the observed data.The peak in both distributions around lower values indicates that the majority of observed and predicted values are concentrated in this range.The predictive distribution's spread captures most of the observed data, indicating a good fit overall.

## Diagnostics

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-dia
#| layout-ncol: 2
#| fig-cap: Markov chain Monte Carlo (MCMC) Convergence Check

plot(model,"trace")
plot(model,"rhat")
``` 
@fig-dia-1 and  @fig-dia-2 indicate that the Bayesian model has converged properly for all parameters. The consistent mixing and stable trajectories across chains suggest that the posterior distributions are well-estimated and that the results can be interpreted with confidence.Since rhat are close to 1,it confirms that Bayesian model has achieved proper convergence, and the parameter estimates are robust and can be confidently interpreted.

# Data Collection for Beef Products

## Introduction to Survey Design

We aim to design a survey to help Canadians better understand the price fluctuations of beef products across the country. This survey will support Canada in gaining a clearer grasp of beef pricing trends to inform policymaking and other decisions.

## Collection methods

Collecting daily product prices from the websites of major supermarkets, such as Voila, T&T, Loblaws, No Frills, Metro, Galleria, Walmart, and Save-On-Foods, provides a valuable way to gather comprehensive pricing information. Focusing on large chain supermarkets ensures better data coverage and consistency. Using an automated approach, we can record daily prices of various products from different supermarkets and consolidate all the data into a single dataset.

In this setup, the primary expense will be software development to automate the data collection and storage process. This system will help streamline data gathering and ensure consistency over time. However, all activities must be conducted with the explicit consent of the supermarkets and in full compliance with ethical and legal standards to ensure no infringement on the rights of individuals or groups.This way, we can obtain three pieces of data: the product name, where it is sold, and its price.We can also collaborate with these supermarkets to obtain their beef product pricing information directly.

\newpage

# References

### 2024-12-03 scripts/00-simulate_data.R

@@ -1,0 +1,28 @@
+#### Preamble ####
+# Purpose: Simulates a dataset 
+# Author: Bo Tang
+# Date: 29 November 2024
+# Contact: qinghe.tang@mail.utoronto.ca
+# License: UofT
+# Pre-requisites: The `tidyverse` package must be installed
+
+
+
+#### Workspace setup ####
+library(tidyverse)
+set.seed(682)
+
+
+#### Simulate data ####
+# vendors names
+vendors <- c("TandT","Loblaws")
+
+simulated_data <- tibble(
+  vendor = sample(vendors, size = 1500, replace = TRUE),
+  current_price = round(runif(1500, 1, 70), 3),
+  old_price=round(runif(1500, 1, 70), 3),
+  month = sample(1:12, size = 1500, replace = TRUE)
+)
+#### Save data ####
+write_parquet(simulated_data, "data/00-simulated_data/simulated_data.parquet")
+write_csv(simulated_data, "data/00-simulated_data/simulated_data.csv")

### 2024-12-03 scripts/01-test_simulated_data.R

@@ -1,0 +1,94 @@
+#### Preamble ####
+# Purpose: Tests the simulated dataset.
+# Author: Bo Tang
+# Date: 29 November 2024
+# Contact: rohan.alexander@utoronto.ca
+# License: UofT
+# Pre-requisites: 
+  # - The `tidyverse` package must be installed and loaded
+  # - 00-simulate_data.R must have been run
+
+
+
+#### Workspace setup ####
+library(tidyverse)
+
+analysis_data <- read_parquet("data/00-simulated_data/simulated_data.parquet")
+
+# Test if the data was successfully loaded
+if (exists("analysis_data")) {
+  message("Test Passed: The dataset was successfully loaded.")
+} else {
+  stop("Test Failed: The dataset could not be loaded.")
+}
+
+
+#### Test data ####
+
+# Check if the dataset has 1500 rows
+if (nrow(analysis_data) == 1500) {
+  message("Test Passed: The dataset has 1500 rows.")
+} else {
+  stop("Test Failed: The dataset does not have 1500 rows.")
+}
+
+# Check if the dataset has 3 columns
+if (ncol(analysis_data) == 4) {
+  message("Test Passed: The dataset has 4 columns.")
+} else {
+  stop("Test Failed: The dataset does not have 4 columns.")
+}
+
+# Check unique values
+unique_vendors <- unique(analysis_data$vendor)
+
+# Test if it only contains the specified values
+all_vendors_valid <- all(unique_vendors %in% c("TandT", "Loblaws"))
+if (all_vendors_valid) {
+  print("The 'vendor' column contains only 'TandT' and 'Loblaws'")
+} else {
+  print(paste("The 'vendor' column contains other values:", paste(setdiff(unique_vendors, c("TandT", "Loblaws")), collapse = ", ")))
+}
+
+# Test if the `vendor` column is character
+if (is.character(analysis_data$vendor)) {
+  print("The 'vendor' column is entirely character type")
+} else {
+  print("The 'vendor' column contains non-character types")
+}
+
+# Check numeric type
+all_numeric <- is.numeric(analysis_data$current_price) & is.numeric(analysis_data$old_price)
+
+# Check if all values are greater than 0
+all_positive <- all(analysis_data$current_price > 0, na.rm = TRUE) & all(analysis_data$old_price > 0, na.rm = TRUE)
+
+if (all_numeric & all_positive) {
+  print("'current_price' and 'old_price' are numeric, and all values are greater than 0")
+} else {
[…]

### 2024-12-03 scripts/03-clean_data.R

@@ -1,0 +1,37 @@
+#### Preamble ####
+# Purpose: Cleans the raw data 
+# Author: Bo Tang
+# Date: 26 November 2024
+# Contact: qinghe.tang@mail.utoronto.ca 
+# License: UofT
+# Pre-requisites: 
+# 1.Down load raw data on https://jacobfilipp.com/hammer/
+
+#### Workspace setup ####
+library(tidyverse)
+library(arrow)
+library(janitor)
+library(lubridate)
+
+#### Clean data ####
+raw_data <- read_csv("data/01-raw_data/hammer-4-raw.csv")
+product_data <- read_csv("data/01-raw_data/hammer-4-product.csv")
+
+combine_data <- raw_data %>% 
+  inner_join(product_data, by = c("product_id" = "id")) %>%
+  select(nowtime,vendor,product_id,product_name,brand,current_price,
+         old_price,units,price_per_unit)
+
+clean_data <- combine_data %>% filter(vendor %in% c("TandT","Loblaws")) %>%
+  select(nowtime, vendor, current_price, old_price, product_name) %>%
+  mutate(month = month(nowtime),
+         current_price = parse_number(current_price),
+         old_price = parse_number(old_price)) %>%
+  filter(str_detect(tolower(product_name),"beef")) %>%
+  select(-nowtime) %>%
+  tidyr:: drop_na()
+  
+
+#### Save data ####
+write_csv(clean_data, "data/02-analysis_data/cleaned_data.csv")
+write_parquet(clean_data,"data/02-analysis_data/cleaned_data.parquet")

### 2024-12-03 scripts/05-exploratory_data_analysis.R

@@ -1,0 +1,105 @@
+#### Preamble ####
+# Purpose: Graph may used in paper
+# Author: Bo Tang
+# Date: 27 November 2024
+# Contact: qinghe.tang@mail.utoronto.ca 
+# License: UofT
+# Pre-requisites: 
+# - The `tidyverse` package must be installed and loaded
+# - The `rstanarm` package must be installed and loaded
+# - The `arrow` package must be installed and loaded
+# - The `ggplot2` package must be installed and loaded
+# - The `dplyr` package must be installed and loaded
+
+#### Workspace setup ####
+library(tidyverse)
+library(rstanarm)
+library(arrow)
+library(dplyr)
+library(ggplot2)
+#### Read data ####
+cleaned_data <- read_parquet("data/02-analysis_data/cleaned_data.parquet")
+
+### graph ####
+
+# Load dplyr package
+library(dplyr)
+
+# Group by month and calculate the overall average price
+monthly_price_trend <- cleaned_data %>%
+  group_by(month) %>%
+  summarize(average_price = mean(current_price, na.rm = TRUE), .groups = "drop")
+
+# Load ggplot2 package
+library(ggplot2)
+
+# Plot the overall price trend
+ggplot(monthly_price_trend, aes(x = month, y = average_price)) +
+  geom_line(color = "blue", size = 1.2) +
+  geom_point(color = "blue", size = 3) +
+  labs(
+    title = "Overall Monthly Price Trend",
+    x = "Month",
+    y = "Average Current Price"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 16, face = "bold"),
+    axis.title = element_text(size = 14),
+    axis.text = element_text(size = 12)
+  )
+
+
+# Plot the box plot for price comparison between vendors
+ggplot(cleaned_data, aes(x = vendor, y = current_price, fill = vendor)) +
+  geom_boxplot(outlier.colour = "red", outlier.size = 2) +
+  labs(
+    title = "Price Distribution of Beef Products by Vendor",
+    x = "Vendor",
+    y = "Current Price"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 16, face = "bold"),
+    axis.title = element_text(size = 14),
+    axis.text = element_text(size = 12),
+    legend.position = "none"
+  ) +
+  scale_fill_manual(values = c("Loblaws" = "blue", "TandT" = "green"))  # Customize colors
+
[…]

### 2024-12-03 scripts/06-model_data.R

@@ -1,0 +1,54 @@
+#### Preamble ####
+# Purpose: Models
+# Author: Bo Tang
+# Date: 27 November 2024
+# Contact: qinghe.tang@mail.utoronto.ca 
+# License: UofT
+# Pre-requisites: 
+# - The `tidyverse` package must be installed and loaded
+# - The `rstanarm` package must be installed and loaded
+# - The `arrow` package must be installed and loaded
+# - The `bayesplot` package must be installed and loaded
+
+
+
+#### Workspace setup ####
+if (!requireNamespace("rstanarm", quietly = TRUE)) install.packages("rstanarm")
+
+
+library(tidyverse)
+library(rstanarm)
+library(bayesplot)
+library(arrow)
+#### Read data ####
+cleaned_data <- read_parquet("data/02-analysis_data/cleaned_data.parquet")
+
+### Model data ####
+# Data preprocessing
+cleaned_data$vendor <- as.factor(cleaned_data$vendor)  # Convert vendor to categorical
+cleaned_data$month <- as.factor(cleaned_data$month)    # Convert month to categorical
+
+# Standardize old_price for better scaling
+cleaned_data$old_price_scaled <- scale(cleaned_data$old_price)
+
+# Build the Bayesian linear regression model
+model <- stan_glm(
+  current_price ~ old_price_scaled + vendor + month,
+  data = cleaned_data,
+  family = gaussian(),
+  prior = normal(0, 2.5),        # Set prior for coefficients
+  prior_intercept = normal(0, 10), # Set prior for intercept
+  chains = 4,                    # Number of chains
+  iter = 2000,                   # Number of iterations per chain
+  seed = 123                     # Set random seed for reproducibility
+)
+
+
+
+#### Save model ####
+saveRDS(
+  model,
+  file = "models/beef_product_model.rds"
+)
+
+

### 2024-12-03 paper/paper.qmd
Add files via upload

@@
 The model is a Bayesian linear regression that predicts the current price of beef products.
-It uses the scaled old price old price as a numerical variable and includes vendor and month as categorical variables.
+It uses the month and old price as a numerical variable and includes vendor as categorical variables.
 This setup allows the model to account for the effects of historical prices, differences between supermarkets, and seasonal variations.
@@
 - $\beta_2$ The coefficient for vendor, representing the effect of different vendors on the current price (a categorical variable encoded as dummy variables).
-- $\beta_3$ The coefficient for month, representing the effect of different months on the current price (a categorical variable encoded as dummy variables).
+- $\beta_3$ The coefficient for month, representing the effect of different months on the current price.
 
@@
 This framework also enables us to quantify uncertainty in the predictions through posterior distributions, offering richer insights compared to traditional regression methods.
-Additionally, the inclusion of categorical variables (vendor and month) and a continuous predictor (scaled old prices) makes the model versatile for capturing both fixed and dynamic aspects of pricing.
+Additionally, the inclusion of categorical variables (vendor) and a continuous predictor (old prices and month) makes the model versatile for capturing both fixed and dynamic aspects of pricing.
 These attributes make Bayesian linear regression the optimal choice for this analysis.

### 2024-12-03 other/Model_API/server.R

@@ -1,0 +1,4 @@
+library(plumber)
+
+serve_model <- plumb("plumber.R")
+serve_model$run(port = 8000)

### 2024-12-03 scripts/00-simulate_data.R

@@ -25,4 +25,3 @@ simulated_data <- tibble(
 )
 #### Save data ####
 write_parquet(simulated_data, "data/00-simulated_data/simulated_data.parquet")
-write_csv(simulated_data, "data/00-simulated_data/simulated_data.csv")

### 2024-12-03 scripts/03-clean_data.R

@@ -30,8 +30,6 @@ clean_data <- combine_data %>% filter(vendor %in% c("TandT","Loblaws")) %>%
   filter(str_detect(tolower(product_name),"beef")) %>%
   select(-nowtime) %>%
   tidyr:: drop_na()
-  
 
 #### Save data ####
-write_csv(clean_data, "data/02-analysis_data/cleaned_data.csv")
 write_parquet(clean_data,"data/02-analysis_data/cleaned_data.parquet")

### 2024-12-03 scripts/06-model_data.R

@@ -26,14 +26,14 @@ cleaned_data <- read_parquet("data/02-analysis_data/cleaned_data.parquet")
 ### Model data ####
 # Data preprocessing
 cleaned_data$vendor <- as.factor(cleaned_data$vendor)  # Convert vendor to categorical
-cleaned_data$month <- as.factor(cleaned_data$month)    # Convert month to categorical
+cleaned_data$month <- as.integer(cleaned_data$month)    # Convert month to categorical
 
 # Standardize old_price for better scaling
-cleaned_data$old_price_scaled <- scale(cleaned_data$old_price)
+cleaned_data$old_price <- as.numeric(cleaned_data$old_price)
 
 # Build the Bayesian linear regression model
 model <- stan_glm(
-  current_price ~ old_price_scaled + vendor + month,
+  current_price ~ old_price + vendor + month,
   data = cleaned_data,
   family = gaussian(),
   prior = normal(0, 2.5),        # Set prior for coefficients

### 2024-12-03 other/other/Model_API/plumber.R
Add files via upload

@@ -1,0 +1,45 @@
+library(plumber)
+library(tidyverse)
+
+model <- readRDS("beef_product_model.rds")
+
+version_number <- "0.0.1"
+
+variables <-
+  list(
+    old_price = "product's previous price,numeric variables",
+    vendor = "seller or distributor of the product,TandT and Loblaws.",
+    month = "the month of the year,numeric variable (1 - 12),"
+  )
+
+#* @param old_price
+#* @param vendor
+#* @param month
+#* @get /predict_price
+predict_price <- function(old_price = 10, vendor = "TandT", month = 8) {
+  old_price <- as.numeric(old_price)
+  vendor <- as.character(vendor)
+  month <- as.integer(month)
+  
+  payload <- data.frame(old_price = old_price,
+                        vendor = vendor,
+                        month = month)
+  
+  posterior_samples <- as.matrix(model)
+  
+  beta_1 <- posterior_samples[, "old_price"]
+  beta_2 <- posterior_samples[, "vendorTandT"]
+  beta_3 <- posterior_samples[, "month"]
+  intercept <- posterior_samples[, "(Intercept)"]
+  
+  predicted_price <- intercept + 
+    beta_1 * payload$old_price +
+    beta_2 * ifelse(payload$vendor == "TandT", 1, 0) +
+    beta_3 * payload$month
+  
+  mean_predicted_price <- mean(predicted_price)
+   
+  result <- list("price" = mean_predicted_price)
+  
+  return(result)
+}

### 2024-12-03 other/scripts/00-simulate_data.R

@@ -1,0 +1,27 @@
+#### Preamble ####
+# Purpose: Simulates a dataset 
+# Author: Bo Tang
+# Date: 29 November 2024
+# Contact: qinghe.tang@mail.utoronto.ca
+# License: UofT
+# Pre-requisites: The `tidyverse` package must be installed
+
+
+
+#### Workspace setup ####
+library(tidyverse)
+set.seed(682)
+
+
+#### Simulate data ####
+# vendors names
+vendors <- c("TandT","Loblaws")
+
+simulated_data <- tibble(
+  vendor = sample(vendors, size = 1500, replace = TRUE),
+  current_price = round(runif(1500, 1, 70), 3),
+  old_price=round(runif(1500, 1, 70), 3),
+  month = sample(1:12, size = 1500, replace = TRUE)
+)
+#### Save data ####
+write_parquet(simulated_data, "data/00-simulated_data/simulated_data.parquet")

### 2024-12-03 other/scripts/03-clean_data.R

@@ -1,0 +1,35 @@
+#### Preamble ####
+# Purpose: Cleans the raw data 
+# Author: Bo Tang
+# Date: 26 November 2024
+# Contact: qinghe.tang@mail.utoronto.ca 
+# License: UofT
+# Pre-requisites: 
+# 1.Down load raw data on https://jacobfilipp.com/hammer/
+
+#### Workspace setup ####
+library(tidyverse)
+library(arrow)
+library(janitor)
+library(lubridate)
+
+#### Clean data ####
+raw_data <- read_csv("data/01-raw_data/hammer-4-raw.csv")
+product_data <- read_csv("data/01-raw_data/hammer-4-product.csv")
+
+combine_data <- raw_data %>% 
+  inner_join(product_data, by = c("product_id" = "id")) %>%
+  select(nowtime,vendor,product_id,product_name,brand,current_price,
+         old_price,units,price_per_unit)
+
+clean_data <- combine_data %>% filter(vendor %in% c("TandT","Loblaws")) %>%
+  select(nowtime, vendor, current_price, old_price, product_name) %>%
+  mutate(month = month(nowtime),
+         current_price = parse_number(current_price),
+         old_price = parse_number(old_price)) %>%
+  filter(str_detect(tolower(product_name),"beef")) %>%
+  select(-nowtime) %>%
+  tidyr:: drop_na()
+
+#### Save data ####
+write_parquet(clean_data,"data/02-analysis_data/cleaned_data.parquet")

### 2024-12-03 other/scripts/04-test_analysis_data.R

@@ -1,0 +1,66 @@
+#### Preamble ####
+# Purpose: Tests cleaned_data
+# Author: Bo Tang
+# Date: 26 November 2024 
+# Contact: qinghe.tang@mail.utoronto.ca 
+# License: UofT
+# Pre-requisites: 
+  # - The `tidyverse` package must be installed and loaded
+  # - The `testthat` package must be installed and loaded
+  # - The `arrow` package must be installed and loaded
+  # - 03-clean_data.R must have been run
+
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(testthat)
+library(arrow)
+
+cleaned_data <- read_parquet("data/02-analysis_data/cleaned_data.parquet")
+
+
+#### Test data ####
+
+# Test: Ensure `vendor` column contains only "Loblaws" and "TandT"
+test_that("Vendor column contains only specified vendors", {
+  valid_vendors <- c("Loblaws", "TandT")
+  expect_true(all(cleaned_data$vendor %in% valid_vendors))
+})
+
+# Test: Ensure `vendor` column is a character vector
+test_that("Vendor column is a character vector", {
+  expect_type(cleaned_data$vendor, "character")
+})
+
+# Test: Ensure `current_price` and `old_price` are numeric and all values are positive
+test_that("Current price and old price are numeric and positive", {
+  expect_type(cleaned_data$current_price, "double")
+  expect_type(cleaned_data$old_price, "double")
+  expect_true(all(cleaned_data$current_price > 0))
+  expect_true(all(cleaned_data$old_price > 0))
+})
+
+# Test: Ensure `month` column is numeric and values are between 1 and 12
+test_that("Month column is double and in valid range", {
+  expect_type(cleaned_data$month, "double")
+  expect_true(all(cleaned_data$month >= 1 & cleaned_data$month <= 12))
+})
+
+# Test: Ensure `product_name` column is a character vector
+test_that("Product name column is a character vector", {
+  expect_type(cleaned_data$product_name, "character")
+})
+
+# Test: Ensure there are no missing values in the dataset
+test_that("No missing values in the dataset", {
+  expect_true(all(complete.cases(cleaned_data)))
+})
+
+
+# Test: Ensure `current_price` values are within a reasonable range
+test_that("Summary statistics are within expected range", {
+  price_summary <- summary(cleaned_data$current_price)
+  expect_true(price_summary["Min."] >= 0)
+  expect_true(price_summary["Max."] <= 1000)  # Adjust this maximum as needed
+})

### 2024-12-03 other/Model_API/plumber.R
Delete other directory

@@ -1,45 +1,0 @@
-library(plumber)
-library(tidyverse)
-
-model <- readRDS("beef_product_model.rds")
-
-version_number <- "0.0.1"
-
-variables <-
-  list(
-    old_price = "product's previous price,numeric variables",
-    vendor = "seller or distributor of the product,TandT and Loblaws.",
-    month = "the month of the year,numeric variable (1 - 12),"
-  )
-
-#* @param old_price
-#* @param vendor
-#* @param month
-#* @get /predict_price
-predict_price <- function(old_price = 10, vendor = "TandT", month = 8) {
-  old_price <- as.numeric(old_price)
-  vendor <- as.character(vendor)
-  month <- as.integer(month)
-  
-  payload <- data.frame(old_price = old_price,
-                        vendor = vendor,
-                        month = month)
-  
-  posterior_samples <- as.matrix(model)
-  
-  beta_1 <- posterior_samples[, "old_price"]
-  beta_2 <- posterior_samples[, "vendorTandT"]
-  beta_3 <- posterior_samples[, "month"]
-  intercept <- posterior_samples[, "(Intercept)"]
-  
-  predicted_price <- intercept + 
-    beta_1 * payload$old_price +
-    beta_2 * ifelse(payload$vendor == "TandT", 1, 0) +
-    beta_3 * payload$month
-  
-  mean_predicted_price <- mean(predicted_price)
-   
-  result <- list("price" = mean_predicted_price)
-  
-  return(result)
-}

### 2024-12-03 other/Model_API/server.R

@@ -1,4 +1,0 @@
-library(plumber)
-
-serve_model <- plumb("plumber.R")
-serve_model$run(port = 8000)

### 2024-12-03 other/scripts/00-simulate_data.R

@@ -1,27 +1,0 @@
-#### Preamble ####
-# Purpose: Simulates a dataset 
-# Author: Bo Tang
-# Date: 29 November 2024
-# Contact: qinghe.tang@mail.utoronto.ca
-# License: UofT
-# Pre-requisites: The `tidyverse` package must be installed
-
-
-
-#### Workspace setup ####
-library(tidyverse)
-set.seed(682)
-
-
-#### Simulate data ####
-# vendors names
-vendors <- c("TandT","Loblaws")
-
-simulated_data <- tibble(
-  vendor = sample(vendors, size = 1500, replace = TRUE),
-  current_price = round(runif(1500, 1, 70), 3),
-  old_price=round(runif(1500, 1, 70), 3),
-  month = sample(1:12, size = 1500, replace = TRUE)
-)
-#### Save data ####
-write_parquet(simulated_data, "data/00-simulated_data/simulated_data.parquet")

### 2024-12-03 other/scripts/03-clean_data.R

@@ -1,35 +1,0 @@
-#### Preamble ####
-# Purpose: Cleans the raw data 
-# Author: Bo Tang
-# Date: 26 November 2024
-# Contact: qinghe.tang@mail.utoronto.ca 
-# License: UofT
-# Pre-requisites: 
-# 1.Down load raw data on https://jacobfilipp.com/hammer/
-
-#### Workspace setup ####
-library(tidyverse)
-library(arrow)
-library(janitor)
-library(lubridate)
-
-#### Clean data ####
-raw_data <- read_csv("data/01-raw_data/hammer-4-raw.csv")
-product_data <- read_csv("data/01-raw_data/hammer-4-product.csv")
-
-combine_data <- raw_data %>% 
-  inner_join(product_data, by = c("product_id" = "id")) %>%
-  select(nowtime,vendor,product_id,product_name,brand,current_price,
-         old_price,units,price_per_unit)
-
-clean_data <- combine_data %>% filter(vendor %in% c("TandT","Loblaws")) %>%
-  select(nowtime, vendor, current_price, old_price, product_name) %>%
-  mutate(month = month(nowtime),
-         current_price = parse_number(current_price),
-         old_price = parse_number(old_price)) %>%
-  filter(str_detect(tolower(product_name),"beef")) %>%
-  select(-nowtime) %>%
-  tidyr:: drop_na()
-
-#### Save data ####
-write_parquet(clean_data,"data/02-analysis_data/cleaned_data.parquet")

### 2024-12-03 other/scripts/04-test_analysis_data.R

@@ -1,66 +1,0 @@
-#### Preamble ####
-# Purpose: Tests cleaned_data
-# Author: Bo Tang
-# Date: 26 November 2024 
-# Contact: qinghe.tang@mail.utoronto.ca 
-# License: UofT
-# Pre-requisites: 
-  # - The `tidyverse` package must be installed and loaded
-  # - The `testthat` package must be installed and loaded
-  # - The `arrow` package must be installed and loaded
-  # - 03-clean_data.R must have been run
-
-
-
-#### Workspace setup ####
-library(tidyverse)
-library(testthat)
-library(arrow)
-
-cleaned_data <- read_parquet("data/02-analysis_data/cleaned_data.parquet")
-
-
-#### Test data ####
-
-# Test: Ensure `vendor` column contains only "Loblaws" and "TandT"
-test_that("Vendor column contains only specified vendors", {
-  valid_vendors <- c("Loblaws", "TandT")
-  expect_true(all(cleaned_data$vendor %in% valid_vendors))
-})
-
-# Test: Ensure `vendor` column is a character vector
-test_that("Vendor column is a character vector", {
-  expect_type(cleaned_data$vendor, "character")
-})
-
-# Test: Ensure `current_price` and `old_price` are numeric and all values are positive
-test_that("Current price and old price are numeric and positive", {
-  expect_type(cleaned_data$current_price, "double")
-  expect_type(cleaned_data$old_price, "double")
-  expect_true(all(cleaned_data$current_price > 0))
-  expect_true(all(cleaned_data$old_price > 0))
-})
-
-# Test: Ensure `month` column is numeric and values are between 1 and 12
-test_that("Month column is double and in valid range", {
-  expect_type(cleaned_data$month, "double")
-  expect_true(all(cleaned_data$month >= 1 & cleaned_data$month <= 12))
-})
-
-# Test: Ensure `product_name` column is a character vector
-test_that("Product name column is a character vector", {
-  expect_type(cleaned_data$product_name, "character")
-})
-
-# Test: Ensure there are no missing values in the dataset
-test_that("No missing values in the dataset", {
-  expect_true(all(complete.cases(cleaned_data)))
-})
-
-
-# Test: Ensure `current_price` values are within a reasonable range
-test_that("Summary statistics are within expected range", {
-  price_summary <- summary(cleaned_data$current_price)
-  expect_true(price_summary["Min."] >= 0)
-  expect_true(price_summary["Max."] <= 1000)  # Adjust this maximum as needed
-})

### 2024-12-03 other/scripts/05-exploratory_data_analysis.R

@@ -1,105 +1,0 @@
-#### Preamble ####
-# Purpose: Graph may used in paper
-# Author: Bo Tang
-# Date: 27 November 2024
-# Contact: qinghe.tang@mail.utoronto.ca 
-# License: UofT
-# Pre-requisites: 
-# - The `tidyverse` package must be installed and loaded
-# - The `rstanarm` package must be installed and loaded
-# - The `arrow` package must be installed and loaded
-# - The `ggplot2` package must be installed and loaded
-# - The `dplyr` package must be installed and loaded
-
-#### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
-library(arrow)
-library(dplyr)
-library(ggplot2)
-#### Read data ####
-cleaned_data <- read_parquet("data/02-analysis_data/cleaned_data.parquet")
-
-### graph ####
-
-# Load dplyr package
-library(dplyr)
-
-# Group by month and calculate the overall average price
-monthly_price_trend <- cleaned_data %>%
-  group_by(month) %>%
-  summarize(average_price = mean(current_price, na.rm = TRUE), .groups = "drop")
-
-# Load ggplot2 package
-library(ggplot2)
-
-# Plot the overall price trend
-ggplot(monthly_price_trend, aes(x = month, y = average_price)) +
-  geom_line(color = "blue", size = 1.2) +
-  geom_point(color = "blue", size = 3) +
-  labs(
-    title = "Overall Monthly Price Trend",
-    x = "Month",
-    y = "Average Current Price"
-  ) +
-  theme_minimal() +
-  theme(
-    plot.title = element_text(size = 16, face = "bold"),
-    axis.title = element_text(size = 14),
-    axis.text = element_text(size = 12)
-  )
-
-
-# Plot the box plot for price comparison between vendors
-ggplot(cleaned_data, aes(x = vendor, y = current_price, fill = vendor)) +
-  geom_boxplot(outlier.colour = "red", outlier.size = 2) +
-  labs(
-    title = "Price Distribution of Beef Products by Vendor",
-    x = "Vendor",
-    y = "Current Price"
-  ) +
-  theme_minimal() +
-  theme(
-    plot.title = element_text(size = 16, face = "bold"),
-    axis.title = element_text(size = 14),
-    axis.text = element_text(size = 12),
-    legend.position = "none"
-  ) +
-  scale_fill_manual(values = c("Loblaws" = "blue", "TandT" = "green"))  # Customize colors
-
[…]

### 2024-12-03 other/scripts/06-model_data.R

@@ -1,54 +1,0 @@
-#### Preamble ####
-# Purpose: Models
-# Author: Bo Tang
-# Date: 27 November 2024
-# Contact: qinghe.tang@mail.utoronto.ca 
-# License: UofT
-# Pre-requisites: 
-# - The `tidyverse` package must be installed and loaded
-# - The `rstanarm` package must be installed and loaded
-# - The `arrow` package must be installed and loaded
-# - The `bayesplot` package must be installed and loaded
-
-
-
-#### Workspace setup ####
-if (!requireNamespace("rstanarm", quietly = TRUE)) install.packages("rstanarm")
-
-
-library(tidyverse)
-library(rstanarm)
-library(bayesplot)
-library(arrow)
-#### Read data ####
-cleaned_data <- read_parquet("data/02-analysis_data/cleaned_data.parquet")
-
-### Model data ####
-# Data preprocessing
-cleaned_data$vendor <- as.factor(cleaned_data$vendor)  # Convert vendor to categorical
-cleaned_data$month <- as.integer(cleaned_data$month)    # Convert month to categorical
-
-# Standardize old_price for better scaling
-cleaned_data$old_price <- as.numeric(cleaned_data$old_price)
-
-# Build the Bayesian linear regression model
-model <- stan_glm(
-  current_price ~ old_price + vendor + month,
-  data = cleaned_data,
-  family = gaussian(),
-  prior = normal(0, 2.5),        # Set prior for coefficients
-  prior_intercept = normal(0, 10), # Set prior for intercept
-  chains = 4,                    # Number of chains
-  iter = 2000,                   # Number of iterations per chain
-  seed = 123                     # Set random seed for reproducibility
-)
-
-
-
-#### Save model ####
-saveRDS(
-  model,
-  file = "models/beef_product_model.rds"
-)
-
-

### 2024-12-03 scripts/01-test_simulated_data.R
Delete scripts directory

@@ -1,94 +1,0 @@
-#### Preamble ####
-# Purpose: Tests the simulated dataset.
-# Author: Bo Tang
-# Date: 29 November 2024
-# Contact: rohan.alexander@utoronto.ca
-# License: UofT
-# Pre-requisites: 
-  # - The `tidyverse` package must be installed and loaded
-  # - 00-simulate_data.R must have been run
-
-
-
-#### Workspace setup ####
-library(tidyverse)
-
-analysis_data <- read_parquet("data/00-simulated_data/simulated_data.parquet")
-
-# Test if the data was successfully loaded
-if (exists("analysis_data")) {
-  message("Test Passed: The dataset was successfully loaded.")
-} else {
-  stop("Test Failed: The dataset could not be loaded.")
-}
-
-
-#### Test data ####
-
-# Check if the dataset has 1500 rows
-if (nrow(analysis_data) == 1500) {
-  message("Test Passed: The dataset has 1500 rows.")
-} else {
-  stop("Test Failed: The dataset does not have 1500 rows.")
-}
-
-# Check if the dataset has 3 columns
-if (ncol(analysis_data) == 4) {
-  message("Test Passed: The dataset has 4 columns.")
-} else {
-  stop("Test Failed: The dataset does not have 4 columns.")
-}
-
-# Check unique values
-unique_vendors <- unique(analysis_data$vendor)
-
-# Test if it only contains the specified values
-all_vendors_valid <- all(unique_vendors %in% c("TandT", "Loblaws"))
-if (all_vendors_valid) {
-  print("The 'vendor' column contains only 'TandT' and 'Loblaws'")
-} else {
-  print(paste("The 'vendor' column contains other values:", paste(setdiff(unique_vendors, c("TandT", "Loblaws")), collapse = ", ")))
-}
-
-# Test if the `vendor` column is character
-if (is.character(analysis_data$vendor)) {
-  print("The 'vendor' column is entirely character type")
-} else {
-  print("The 'vendor' column contains non-character types")
-}
-
-# Check numeric type
-all_numeric <- is.numeric(analysis_data$current_price) & is.numeric(analysis_data$old_price)
-
-# Check if all values are greater than 0
-all_positive <- all(analysis_data$current_price > 0, na.rm = TRUE) & all(analysis_data$old_price > 0, na.rm = TRUE)
-
-if (all_numeric & all_positive) {
-  print("'current_price' and 'old_price' are numeric, and all values are greater than 0")
-} else {
[…]

### 2024-12-03 paper/paper.qmd
Add files via upload

@@
 
+## Estimand
+
+We want to estimate our current price using vendor, month, and old price.After a quick review of the raw data, I believe that the estimated current price should ultimately be lower than the old price.
+
 # Data {#sec-data}
@@
 ## Overview
-The data for this study came from Project Hammer[@PG].The datasets were cleaned and analysed using the statistical programming software `R` [@citeR] along with the help of `tidyverse` [@citeTidyverse], `knitr` [@citeKnitr], `ggplot2` [@citeGgplot], `here` [@citeHere], `dplyr` [@citeDplyr], `rstanarm` [@citeRstanarm], `arrow` [@citeArrow], `broom.mixed` [@citeBroomMixed] and `kableExtra` [@citeKableExtra].The raw data covers eight major large supermarkets in Canada and the changes in their products between February 28, 2024, and November 26, 2024.
+The data for this study came from Project Hammer[@PG].The datasets were cleaned and analysed using the statistical programming software `R` [@citeR] along with the help of `tidyverse` [@citeTidyverse], `knitr` [@citeKnitr], `ggplot2` [@citeGgplot], `here` [@citeHere], `dplyr` [@citeDplyr], `rstanarm` [@citeRstanarm], `arrow` [@citeArrow], `broom.mixed` [@citeBroomMixed] and `kableExtra` [@citeKableExtra].The raw data covers eight major large supermarkets in Canada and the changes in their products between February 28, 2024, and November 26, 2024.In the following section, I will explain the components of my dataset, the time period it covers, and other detailed information.
 
@@
 
+- **Nowtime:** Timestamp indicating when the data was gathered.
+
+- **Vendor:** 	One of the 7 grocery vendors.
+
+- **Product Id:** An internal ID for a product - it represents 1 unique product at 1 vendor. It will allow you to track prices on the same product over time.
+
+- **Product Name:** Product name. May include Brand, may include Units in it.
+
+- **Brand:** Brand name. May be blank for some vendors.
+
+- **Units:** Units (grams, kg, number of items in package). May be blank for some vendors/products.
+
+- **Current Price:** 	Price at time of extract.
+
+- **Old Price:** An "old" struck-out price. This indicates that there was a Sale on. This is how you can differentiate a price-drop advertised as a Sale vs. a "quiet" decrease without a Sale.
+
+- **Price Per Unit:** Price per unit, as shown on the vendor website. May not be consistent with real calculation of "current price" divided by "units".
+
+- **Other:** 	Other details that appeared on the listing. Values may be "Out of stock", "SALE", "Best seller", "$5.00 MIN 2".
+
 ## Outcome variables
@@
 It serves as a critical metric for understanding pricing strategies, consumer behavior, and market trends.
-By analyzing current_price, we can evaluate the impact of factors such as discounts (old price), vendor differences, and temporal trends (e.g., month) on product pricing.The line graph [@fig-current] illustrates the average monthly current_price trend across the dataset.
+By analyzing current price, we can evaluate the impact of factors such as discounts (old price), vendor differences, and temporal trends (e.g., month) on product pricing.The line graph [@fig-current] illustrates the average monthly current price trend across the dataset.
 The most notable pattern is the significant drop in prices between months 6 and 8, reaching the lowest average in month 8.
@@
 The decline in prices during the mid-year months could indicate promotional events, seasonal sales, or a decrease in consumer demand during that period.
-Conversely, the rise in prices from months 9 to 11 may correspond to increased demand, possibly due to holiday preparations or end-of-year market adjustments.
+Conversely, the rise in prices from months 9 to 11 may correspond to increased demand, possibly due to holiday preparations or end of year market adjustments.
 
@@
 
+The summary shows that the current_price in the dataset ranges from 0.39 to 101.15, with most prices concentrated in the lower range, as indicated by a median of 6.87 and a third quartile of 10.99.
+The average price is 9.56, while the standard deviation of 11.39 suggests significant variability, likely influenced by a few high outliers.
+```{r}
+#| label: tbl-summary
+#| fig-cap: Summary Statistics for Current Price
+#| echo: false
+
+summary_stats <- summary(cleaned_data$current_price)
+std_dev <- sd(cleaned_data$current_price, na.rm = TRUE)
+
+stats_table <- data.frame(
+  Statistic = c("Minimum", "1st Quartile", "Median", "Mean", "3rd Quartile", "Maximum", "Standard Deviation"),
+  Value = c(
+    summary_stats["Min."],
+    summary_stats["1st Qu."],
+    summary_stats["Median"],
+    summary_stats["Mean"],
+    summary_stats["3rd Qu."],
+    summary_stats["Max."],
+    std_dev
+  )
+)
+
+kable(stats_table)
+
+```
 ## Predictor variables
@@
 **Old price**:This variable represents the product's previous price.
-It serves as an indicator of discounts or price changes, which are key factors in determining the current_price.
+It serves as an indicator of discounts or price changes, which are key factors in determining the current price.
 It provides a direct measure of pricing adjustments over time.
@@
 Additionally, some data in the dataset contained missing values.
-However, when reviewing the raw data, I observed that for the same product within the same month, the current_price and old_price were relatively consistent.
+However, when reviewing the raw data, I observed that for the same product within the same month, the current price and old price were relatively consistent.
 For example, if there was complete data on the 1st of the month, missing data on the 4th, and complete data again on the 10th, the values on the 1st and the 10th were identical.
@@
 
-## Collection methods
+## idealize Collection methods
 
@@
 
-In this setup, the primary expense will be software development to automate the data collection and storage process.
-This system will help streamline data gathering and ensure consistency over time.
-However, all activities must be conducted with the explicit consent of the supermarkets and in full compliance with ethical and legal standards to ensure no infringement on the rights of individuals or groups.This way, we can obtain three pieces of data: the product name, where it is sold, and its price.We can also collaborate with these supermarkets to obtain their beef product pricing information directly.
+The primary expense in this setup will be software development to automate the data collection and storage process.
+This system will streamline data gathering and ensure consistency over time.
+To achieve this, all activities must be conducted with the explicit consent of the supermarkets and in full compliance with ethical and legal standards, ensuring no infringement on the rights of individuals or groups.
+Through this system, we can obtain three key pieces of data: the product name, its location of sale, and its price.
+Additionally, we can collaborate with supermarkets to directly access their beef product pricing information.
+By complementing this with daily sales data, we can better analyze the demand for beef products.Building on this, we will divide the analysis into two major sections: rural and urban areas.
+The datasets for these two categories will be analyzed separately, as the demand and market size for beef products differ significantly between rural and urban areas.
+This approach will allow us to conduct a more targeted analysis of each group.
+
+## Survey Questionnaire
+
+With the market survey and data collection complete, we will have gathered enough information to proceed.
+Next, our focus will shift to understanding the people themselves.
+By analyzing demand for beef products across different demographics—such as age, region, and gender—we aim to study how demand varies among different groups.
+This will allow us to gain deeper insights into consumer preferences and behaviors.
+
+Section 1: Personal Information
+
+1. Gender
+
+ - Male
+ - Female
+ - Other/Prefer not to say
+
+2. Age Group
+
+ - Under 18
+ - 18-24
+ - 25-34
+ - 35-44
+ - 45-54
+ - 55-64
+ - 65 and above
+
+3. Location
+
+- Province/Territory:
+(Drop-down menu or text input for respondents to specify their province/territory in Canada)
+
+4. Area:
+ - Urban
+ - Rural
+
+Section 2: Beef Product Demand
+
+1.How would you describe your demand for beef products?
+
+ - High demand (consume beef frequently, buy large quantities)
+ - Moderate demand (consume beef occasionally, buy moderate quantities)
+ - Low demand (rarely consume beef, buy small quantities)
+ - No demand (do not consume beef)
+
+2.How often do you purchase beef products?
+
+ - Daily
+ - 2-3 times a week
+ - Weekly
+ - Biweekly
+ - Monthly
+ - Rarely/Never
+
+Section（Optional） 3： Additional Feedback
+
+1.Are there any factors that influence your beef product purchasing decisions?
+
+ - (e.g., price, availability, dietary preferences, cultural practices, etc.)
+
+2.Would you like to be contacted for future surveys or updates on this research?
+
+ - Yes
+ - No
 

### 2024-12-03 scripts/06-model_data.R

@@ -1,0 +1,54 @@
+#### Preamble ####
+# Purpose: Models
+# Author: Bo Tang
+# Date: 27 November 2024
+# Contact: qinghe.tang@mail.utoronto.ca 
+# License: UofT
+# Pre-requisites: 
+# - The `tidyverse` package must be installed and loaded
+# - The `rstanarm` package must be installed and loaded
+# - The `arrow` package must be installed and loaded
+# - The `bayesplot` package must be installed and loaded
+
+
+
+#### Workspace setup ####
+if (!requireNamespace("rstanarm", quietly = TRUE)) install.packages("rstanarm")
+
+
+library(tidyverse)
+library(rstanarm)
+library(bayesplot)
+library(arrow)
+#### Read data ####
+cleaned_data <- read_parquet("data/02-analysis_data/cleaned_data.parquet")
+
+### Model data ####
+# Data preprocessing
+cleaned_data$vendor <- as.factor(cleaned_data$vendor)  # Convert vendor to categorical
+cleaned_data$month <- as.integer(cleaned_data$month)    # Convert month to categorical
+
+# Standardize old_price for better scaling
+cleaned_data$old_price <- as.numeric(cleaned_data$old_price)
+
+# Build the Bayesian linear regression model
+model <- stan_glm(
+  current_price ~ old_price + vendor + month,
+  data = cleaned_data,
+  family = gaussian(),
+  prior = normal(0, 2.5),        # Set prior for coefficients
+  prior_intercept = normal(0, 10), # Set prior for intercept
+  chains = 4,                    # Number of chains
+  iter = 2000,                   # Number of iterations per chain
+  seed = 123                     # Set random seed for reproducibility
+)
+
+
+
+#### Save model ####
+saveRDS(
+  model,
+  file = "models/beef_product_model.rds"
+)
+
+

### 2024-12-03 paper/paper.qmd
Add files via upload

@@
 
-The summary shows that the current_price in the dataset ranges from 0.39 to 101.15, with most prices concentrated in the lower range, as indicated by a median of 6.87 and a third quartile of 10.99.
+The summary shows that the current price in the dataset ranges from 0.39 to 101.15, with most prices concentrated in the lower range, as indicated by a median of 6.87 and a third quartile of 10.99.
 The average price is 9.56, while the standard deviation of 11.39 suggests significant variability, likely influenced by a few high outliers.

### 2024-12-04 paper/paper.qmd
Add files via upload

@@
 thanks: "Code and data are available at: [https://github.com/Botangeric/Beef-Pricing-Dynamics-in-Canadian-Supermarkets)."
-date: today
+date: 3 December 2024
 date-format: long
